---
title: "Report"
data: Sys.Date()
output: 
 html_document:
    toc: true
    toc_depth: 3
params:
 infoReport: 1
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  echo = FALSE,
  comment = "##",
  results = TRUE,
  warning = FALSE,
  message = FALSE,
  highlight = TRUE,
  background = 'grey',
  fig.cap = TRUE,
  out.height = "\\textheight",
  out.width = "\\textwidth"
)
#knitr::opts_chunk$set(out.height = "\\textheight",  ,
#                      out.extra = "keepaspectratio=false")
```

```{r setup, include = FALSE}
library(connector)
library(parallel)
detectCores(logical = FALSE) -> nworkers
nworkers <- nworkers - 1 # just for my laptop to survive 

p = params$infoReport$p
G = params$infoReport$G
data.selected = params$infoReport$data
f.selected = params$infoReport$feature
clusterdata = params$infoReport$clusterdata

 
```

# Recap
The following parameters value has been selected:

 1. the number of basis spline,
 `r if(!is.null(p)){paste("p = ",p) }else{ paste("p was not selected ")} ` ;
 2. the number of clusters, 
 `r if(!is.null(params$infoReport$G)){paste("G = ",params$infoReport$G) }else{ paste("G was not selected ")} ` .
 
# Data overview

Number of curves: 
 `r  `

# Data visualisation

```{r , fig.height = 3, fig.width = 7, fig.align = "center", fig.cap="Sampled curves coloured by  feature selected."}

GrowPlot<-GrowthCurve(data.selected,
                      feature = f.selected)

GrowPlot$GrowthCurve_plot

```

```{r , fig.height = 3, fig.width = 7, fig.align = "center", fig.cap="Time grid."}

Timegrid <- TimeGridDensity(data = data.selected)
Timegrid$TimeGrid_plot

```

```{r , fig.height = 3, fig.width = 7, fig.align = "center", fig.cap="Time grid."}
if(!is.null(params$infoReport$truncTime) ){
  data.selected <- DataTruncation(data = data.selected,
               truncTime = params$infoReport$truncTime,
               feature =  f.selected)
  print(data.selected$GrowthCurve_plot)
}


```



# Paramenters selection


```{r CrossLL, fig.height = 3, fig.width = 7, fig.align = "center"}

if(is.character(params$infoReport$CrossLL)){
  
  readInputRdsFile = function(input_rds){
    input = tryCatch(readRDS(input_rds), 
    error = function(c) stop("The input *rds is invalid. Please fix your input file.")
    )
  }
  readInputRdsFile(params$infoReport$CrossLL)
  
}else if(is.vector(params$infoReport$CrossLL)){
  
  CrossLogLike<-BasisDimension.Choice(data.selected,
                                    p = params$infoReport$CrossLL,
                                    Cores = nworkers)
  CrossLogLike$CrossLogLikePlot
  CrossLogLike$KnotsPlot
  
}

```


The number of basis spline (p) is: 
 `r paste("p = ",p)` .
 

 
```{r FDBindexes ,  fig.align = "center"}
if(!is.null(clusterdata)){
  IndexesPlot.Extrapolation(clusterdata)-> indexes
  
  print(indexes$Plot)
  
  knitr::kable(indexes$IndexesValues$fDB)
}

```

# Cluster plots

```{r ClusterPlots, fig.height = 3, fig.width = 7, fig.align = "center"}

if(!is.null(G) && !is.null(clusterdata) ) {
  ConsMatrix.Extrapolation(clusterdata,
                           data = data.selected)-> ConsInfo

  for( g in G){
    print(ConsInfo[[paste0("G",g)]]$ConsensusPlot)
    clusterdata.selected <- MostProbableClustering.Extrapolation(stability.list = clusterdata,
                                                                 G = g)
    FMplots<- ClusterWithMeanCurve(clusterdata = clusterdata.selected,
                              data= data.selected,
                              feature = f.selected)

    print(FMplots$plotMeanCurve)
    print(FMplots$plotsCluster$ALL)
  }
  
}

```



<!-- ```{r , fig.height = 3, fig.width = 7, fig.align = "center"} -->

<!-- if(!is.null(params$infoReport$DiscriminantPlot)) params$infoReport$DiscriminantPlot -->
<!-- if(!is.null(params$infoReport$DiscriminantPlotF)) params$infoReport$DiscriminantPlotF -->

<!-- ``` -->

<!-- # Spline fitting -->

<!-- ```{r , fig.height = 3, fig.width = 7, fig.align = "center"} -->

<!-- if(!is.null(params$infoReport$FCMplots)){ -->

<!-- for(i in lengeth(params$infoReport$FCMplots$spline.plots)) params$infoReport$FCMplots$spline.plots[[i]] -->

<!--   } -->

<!-- ``` -->

